I am a title (RO SLAM Methods/Implementation Survey)

### 2018-01-16 Paper.tex
Added figure path
added path to figures in Figure folder to tex file

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
%\graphicspath{Figures}

@@

Djugash proposes an extension to EKF called relative-over parametrized (ROP) EKF. This extension uses specific parameterization to  better represent the range only data utilized in RO-SLAM. \cite{Djugash2008}. ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates. The method provided improved results over EKF when sparse range measurement of data association errors were present. Herranz presents a comparison of the ROP-EKF method presented by Djugash \cite{Djugash2008},to a smoothing and mapping method presented by Dellaert \cite{Dellaert2006}. Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF. \cite{Herranz2014}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\graphicspath{{Figures/}}

@@

Djugash proposes an extension to EKF called relative-over parametrized (ROP) EKF. This extension uses specific parameterization to  better represent the range only data utilized in RO-SLAM. \cite{Djugash2008}. ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates.
\begin{figure}[h!]
	\centering
	\includegraphics[width=90mm]{ROP_djugash.png}
	\caption{True and approximated distributions with one range observation (Top Row) and two observations from different locations (Bottom Row). True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated. \cite{Djugash2008}} %THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
	\label{ROP_djugash}
\end{figure}

The method provided improved results over EKF when sparse range measurement of data association errors were present. Herranz presents a comparison of the ROP-EKF method presented by Djugash \cite{Djugash2008},to a smoothing and mapping method presented by Dellaert \cite{Dellaert2006}. Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF. \cite{Herranz2014}
